### 2017-10-17 NLO.tex
updated TreeLevelPlots

\section{Squark Production at One-Loop}
This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$. To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}. After that, the setup of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$, which has been performed by a \texttt{C++} program, is explained. This includes a remark on how the calculation was sped up. Finally the results of the computation are presented in the form of $K$-factors. These are then compared to the ones in the MSSM before the thesis closes with a discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.

@@

	\draw[fill=black] (80:1.1) circle (.01);
	\draw[fill=black] (90:1.1) circle (.01);
	\draw[fill=black] (100:1.1) circle (.01);
	\draw[fill=black] (-80:1.1) circle (.01);
	\draw[fill=black] (-90:1.1) circle (.01);
	\draw[fill=black] (-100:1.1) circle (.01);
\end{tikzpicture}.
\end{center}
\end{figure}\\
Now it becomes clear, why the renormalization in the on-shell scheme
\begin{align}
\left.\frac{\partial \Sigma(p^2)}{\partial p^2}\right|_{p^2 = m^2} \stackrel{!}{=} 0
\end{align}
introduces no further modification, when turning from the Green function to the S-matrix-element. The residues of the propagator are $Z = 1$ in on-shell renormalization. Furthermore the on-shell condition for the mass renormalization
\begin{align}
\left.\Sigma(p^2)\right|_{p^2 = m^2} = 0
\end{align}
means that the physical mass equals the tree level mass.

@@

	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}|^2}$};
	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}|^2}$};	

@@

	\node [block6a] at (7.5,-10.7) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};

>>>>

\section{Squark Production at One-Loop}
This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$. To comment on the calculation, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM} and why loop corrections of external particles (see caption of {fig:1loopdiagrams}) are not taken into account. After that, the setup of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$, which has been performed by a \texttt{C++} program, is explained. This includes a remark on how the calculation was sped up. Finally the results of the computation are presented in the form of $K$-factors. These are then compared to the ones in the MSSM before the thesis closes with a discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.

@@

	\draw[fill=black] (80:1.1) circle (.01);
	\draw[fill=black] (90:1.1) circle (.01);
	\draw[fill=black] (100:1.1) circle (.01);
	\draw[fill=black] (-80:1.1) circle (.01);
	\draw[fill=black] (-90:1.1) circle (.01);
	\draw[fill=black] (-100:1.1) circle (.01);
\end{tikzpicture}.
\end{center}
\end{figure}\\
Now it becomes clear, why the renormalization in the on-shell scheme
\begin{align}
\left.\frac{\partial \Sigma(p^2)}{\partial p^2}\right|_{p^2 = m^2} \stackrel{!}{=} 0
\end{align}
introduces no further modification, when turning from the Green function to the S-matrix-element. The residues of the propagator are $Z = 1$ in on-shell renormalization. Furthermore the on-shell condition for the mass renormalization
\begin{align}
\left.\Sigma(p^2)\right|_{p^2 = m^2} = 0
\end{align}
means that the physical mass equals the tree level mass.\\
Finally one can conclude that loop-corrections of the S-matrix-element correspond only to internal loops, i.e. self-energies of external particles do not contribute.%as the S-matrix-element is proportional to the amputated Green function

@@

	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}}|^2$};
	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}}|^2$};	

@@

	\node [block6a] at (7.5,-10.7) (Sigma) {$\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}$};

### 2017-10-17 RSymmetry.tex
updated TreeLevelPlots

Apart from these extensions $R$-symmetry also forbids terms which are allowed by supersymmetry. For the above choice of $R$-charges the $\mu$-term in \eqref{eq:W_MSSM} and the $A$-terms in the last line of \eqref{eq:L_soft} are absent in the MRSSM. Inspecting eq. \eqref{eq:off_diagonal} implies that there is no squark mixing in the MRSSM. As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ in the MSSM are suppressed in the MRSSM\cite{Kribs:2007ac}. Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}. Finally the production cross section of strongly interacting particles is suppressed\cite{Kribs:2012gx, Kribs:2013oda}. It is this last feature which is going to be observed further in this thesis. To this end the colored sector of the MRSSM is now considered in more detail.

@@

The soft breaking Lagrangian accounts for the squark, gaugino and scalar gluon masses. These mass terms arise from a hidden sector spurion. For gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$. After integrating out the spurion one obtains\cite{Fox:2002bu, Diessner:2015bna}

>>>>

Apart from these extensions $R$-symmetry also forbids terms which are allowed by supersymmetry. For the above choice of $R$-charges the $\mu$-term in \eqref{eq:W_MSSM} and the $A$-terms in the last line of \eqref{eq:L_soft} are absent in the MRSSM. Inspecting eq. \eqref{eq:off_diagonal} implies that there is no squark mixing in the MRSSM. As a consequence terms which allow flavor violating processes like $\mu \to e \gamma$ in the MSSM are suppressed in the MRSSM\cite{Kribs:2007ac}. Quite interestingly Dirac gauginos can be heavier than Majorana gauginos without being less natural in view of the hierarchy problem\cite{Fox:2002bu, Nelson:2002ca, Kribs:2012gx, Hardy:2013ywa}. This is because the (one-loop) beta function of the squark mass does not depend on the gluino mass.\footnote{If $m_{\tilde{q}}$ is evolved via renormalization group equation to smaller energies, $m_{\tilde{g}}$ is in the MSSM responsible for an increase of $m_{\tilde{q}}$. At a high energy scale, all masses of supersymmetric particles are considered as equal, which forces $m_{\tilde{g}}$ in the MSSM to be ``small'' in order to ensure a not too high squark mass at the EWSB-scale. A too high $m_{\tilde{q}}$ would spoil the solution to the hierarchy problem. This $m_{\tilde{g}}$ dependence is absent in the MRSSM, which imposes no restriction on $m_{\tilde{g}}$, in this respect.}
Finally the production cross section of strongly interacting particles is suppressed\cite{Kribs:2012gx, Kribs:2013oda}. It is this last feature which is going to be observed further in this thesis. To this end the colored sector of the MRSSM is now considered in more detail.

@@

The soft breaking Lagrangian accounts for the squark, gaugino and scalar gluon masses. These mass terms arise from a hidden sector spurion. For gauginos the D-type spurion is given by $\hat{W}_\alpha^\prime = \theta_\alpha D$ and mediates super symmetry breaking at the mediation scale $M$: $\int\mathrm{d}\theta^2\frac{\hat{W}_\alpha^\prime}{M}W_s^\alpha \hat{O}$. After integrating out the spurion one obtains\cite{Fox:2002bu, Diessner:2014ksa}

### 2017-10-17 Renormalization.tex
updated TreeLevelPlots

is the supersymmetry restoring renormalization constant. Note the sign within this definition in comparison to eq. \eqref{eq:GammaCtRestore}. The only point where particularly care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms:

@@

\caption{Diagrammatic contributions to the self-energy of the squark at 1-loop level}\label{fig:GluinoSE}

@@

&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( ((n_f-1))  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\

@@

&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}

@@

&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_0(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}.

@@

\begin{table}[!htpb]
\begin{center}
\begin{tabular}{c?c?c}
$\epsilon^i$ & Contribution & Settings in \texttt{FormCalc}\\
\hlinewd{2pt}
$\epsilon^{-2}$ & $\epsilon^{-2}$ & (\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$) \\
\hline
$\epsilon^{-1}$ & $\epsilon^{-1}$ & (\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$) \\
  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to -2$) \\
  & & $-$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$)\\
\hline
$\epsilon^{0}$ & $\epsilon^{0}$ & (\texttt{SetLambda} $\to 0$, \texttt{Dminus4} $\to 0$) \\
  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to -2$) \\
  & & $-$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$)
\end{tabular}
\caption{The table shows what settings need to be adjusted in \texttt{FormCalc} to extract double and single poles as well as finite terms of an expression in \texttt{Mathematica} which contains loop-integrals.}\label{tab:poles}
\end{center}
\end{table}

>>>>

is the supersymmetry restoring renormalization constant. Note the sign within this definition in comparison to eq. \eqref{eq:GammaCtRestore}. The only point where particular care is required is the coupling: The  gauge coupling $g_s$ and the Yukawa coupling $\hat{g}_s$ receive different supersymmetry restoring counterterms:

@@

\caption{Diagrammatic contributions to the self-energy of the gluino at 1-loop level}\label{fig:GluinoSE}

@@

&+ 4T(F) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left( (n_f-1)  B_1(p^2,0,m_{\tilde{q}}^2) +  B_1(p^2,m_t^2,m_{\tilde{q}}^2) \right)\nonumber\\

@@

&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}

@@

&-4 C(A) m_{\tilde{g}}^2 \frac{\partial}{\partial p^2} \left.\left( -B_0(p^2,0,m_{\tilde{g}}^2) + B_1(p^2,0,m_{\tilde{g}}^2) \right)\right]_{p^2=m_{\tilde{g}}^2}.

@@

\begin{table}[!htpb]
\begin{center}
\begin{tabular}{c?c?c}
$\epsilon^i$ & Contribution & Settings in \texttt{FormCalc}\\
\hlinewd{2pt}
$\epsilon^{-2}$ & $\epsilon^{-2}$ & (\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$) \\
\hline
$\epsilon^{-1}$ & $\epsilon^{-1}$ & (\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$) \\
  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-2}$ & $+$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to -2$) \\
  & & $-$(\texttt{SetLambda} $\to -2$, \texttt{Dminus4} $\to 0$)\\
\hline
$\epsilon^{0}$ & $\epsilon^{0}$ & (\texttt{SetLambda} $\to 0$, \texttt{Dminus4} $\to 0$) \\
  & $+\mathcal{O}(\epsilon)\cdot\epsilon^{-1}$ & $+$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to -2$) \\
  & & $-$(\texttt{SetLambda} $\to -1$, \texttt{Dminus4} $\to 0$)
\end{tabular}
\caption{The table shows what settings need to be adjusted in \texttt{FormCalc} to extract double and single poles as well as finite terms of an expression in \texttt{Mathematica} which contains loop-integrals.}\label{tab:poles}
\end{center}
\end{table}

### 2017-10-17 Standardmodel.tex
updated TreeLevelPlots

[T^a,T^b] = if_{abc}T^c,

@@

right-handed leptons & $e_{iR}$ & - & 0 & $+1$ & $+1$\\

@@

\subsubsection*{The Force Particles}
\begin{table}[H]
\begin{center}
\begin{tabular}{c|c|c?c|c|c}
\multicolumn{3}{c?}{Before EWSB} & \multicolumn{3}{c}{After EWSB}\\
\hlinewd{2pt}
Group & Coupling Constant & Gauge Field & Coupling Constant & Gauge Field & Particle\\
\hlinewd{2pt}
$SU(3)_C$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & gluon\\
$SU(2)_L$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
 & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ boson\\
$U(1)_Y$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & photon
\end{tabular}
\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB), see section \ref{sec:EWSB}. The Gluon field is not affected by EWSB. $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields. $c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}.}\label{tab:force_particles}
\end{center}
\end{table}
The force particles are described by gauge fields. The gauge field of $SU(3)_C$ is the gluon field. Because the $SU_C(3)$ has eight generators there are eight gluons. Their coupling constant is denoted with $g_s$.\\
For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved. They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU_L(2)_L$ and $U_Y(1)_Y$ respectively. This mixing procedure is explained in section \ref{sec:EWSB}.\\
For the moment being, the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
\begin{align}
\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} + \overline{d}_{iR} i \slashed{D} d_{iR} \right),
\end{align}
where $i \in \left\{1,2,3\right\}$ labels the generations of matter. The gauge covariant derivative is given by
\begin{align}
D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu,
\end{align}
where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can also be found in table \ref{tab:SMfieldcontent}.
The kinetic terms of the gauge fields are given by
\begin{align}
\mathcal{L}_{\mathrm{gauge}} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
\end{align}

>>>>

[T^a,T^b] = if_{abc}T^c,\label{eq:struc_const}

@@

right-handed leptons & $e_{iR}$ & - & 0 & $-1$ & $+1$\\

@@

\subsubsection*{The Force Particles}
\begin{table}[H]
\begin{center}
\begin{tabular}{c|c|c?c|c|c}
\multicolumn{3}{c?}{Before EWSB} & \multicolumn{3}{c}{After EWSB}\\
\hlinewd{2pt}
Group & Coupling Constant & Gauge Field & Coupling Constant & Gauge Field & Particle\\
\hlinewd{2pt}
$SU(3)_C$ & $g_s$ & $G^a_\mu$ & $g_s$ & $G^a_\mu$ & gluon\\
$SU(2)_L$ & $g_w$ & $W^b_\mu$ & $g_W = \sqrt{2}g_w$,  &  $W^\pm_\mu$,  & $W^\pm$,  \\
 & & & $g_Z = \sqrt{g_w^2 + g_Y^2}$ & $Z^0_\mu$ & $Z^0$ boson\\
$U(1)_Y$ & $g_Y$ & $B_\mu$ & $e = g_Y\cdot c_w$ & $A_\mu$ & photon
\end{tabular}
\caption{The gauge fields and their coupling constants before and after electro weak symmetry breaking (EWSB), see section \ref{sec:EWSB}. The Gluon field is not affected by EWSB. $a = 1,\hdots 8$ and $b=1,2,3$ label the number of gauge fields. $c_w$ is the cosine of the electroweak mixing angle defined in \ref{sec:EWSB}.}\label{tab:force_particles}
\end{center}
\end{table}
The force particles are described by gauge fields. The gauge field of $SU(3)_C$ is the gluon field. Because the $SU_C(3)$ has eight generators there are eight gluons. Their coupling constant is denoted with $g_s$.\\
For the other force particles in the Standard Model - the $W^\pm$ bosons, the $Z_0$ boson and the photon the situation is slightly more involved. They are obtained as a mixture of the $W^b_\mu$ ($b=1,2,3$) and the $B_\mu$ field which are the gauge fields of $SU(2)_L$ and $U(1)_Y$ respectively. This mixing procedure is explained in section \ref{sec:EWSB}.\\
For the moment being, the coupling constants and gauge fields before and after this mixing are quoted in table \ref{tab:force_particles}.\bigbreak
The Lagrangian of the SM is built up by qualitatively different terms. Firstly there are the kinetic and minimal coupling terms of the matter fields 
\begin{align}
\mathcal{L}_{\mathrm{matter}} =  \sum_{i=1}^3 \left( \overline{\ell}_{iL} i \slashed{D} l_{iL} + \overline{e}_{iR} i \slashed{D} e_{iR} + \overline{q}_{iL} i \slashed{D} q_{iL} + \overline{u}_{iR} i \slashed{D} u_{iR} + \overline{d}_{iR} i \slashed{D} d_{iR} \right),
\end{align}
where $i \in \left\{1,2,3\right\}$ labels the generations of matter. The gauge covariant derivative is given by
\begin{align}
D_\mu = \partial_\mu + i g_Y\frac{\hat{Y}}{2} +ig_w \vec{\tau}\cdot \vec{W}^\mu + i g_s T^a G_a^\mu,
\end{align}
where for each field the corresponding representation (fundamental or trivial) of the gauge group is to be inserted (see table \ref{tab:SMfieldcontent}). The hypercharge operator $\hat{Y}$ gives the eigenvalue of the hypercharge of the field it is applied to. These can also be found in table \ref{tab:SMfieldcontent}.
The kinetic terms of the gauge fields are given by
\begin{align}
\mathcal{L}_{\mathrm{gauge}} = -\frac{1}{4}F^{\mu\nu}F_{\mu\nu} - \frac{1}{4}W^{a\mu\nu}W^a_{\mu\nu} - \frac{1}{4}G^{a\mu\nu}G^a_{\mu\nu}.
\end{align}

### 2017-10-17 Summary.tex
updated TreeLevelPlots

As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that they are slightly larger in the MRSSM. But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\

>>>>

As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that they are slightly larger in the MRSSM. But since the tree-level cross section of squark production in the MRSSM is, depending on the choice of squark and gluino mass, up to a factor of about eight smaller than in the MSSM, this renders the MRSSM, in this respect, to a perfectly viable extension of the Standard Model.\\
